

```{r}
data = read.csv('/Users/joesiezheng/Dropbox/Mac/Desktop/Framework\ and\ method\ 1/kaggle/rentlala2021/analysisData.csv')

scoringData = read.csv('/Users/joesiezheng/Dropbox/Mac/Desktop/Framework\ and\ method\ 1/kaggle/rentlala2021/scoringData.csv')
```





######## transforming t/f to 1/0 and converting categorical variables to numeric variables #########

```{r}
data$host_is_superhost[data$host_is_superhost == "t"] = 1
data$host_is_superhost[data$host_is_superhost == "f"] = 0
scoringData$host_is_superhost[scoringData$host_is_superhost == "t"] = 1
scoringData$host_is_superhost[scoringData$host_is_superhost == "f"] = 0
data$host_is_superhost = as.numeric(data$host_is_superhost)
scoringData$host_is_superhost = as.numeric(scoringData$host_is_superhost)


data$host_has_profile_pic[data$host_has_profile_pic == "t"] = 1
data$host_has_profile_pic[data$host_has_profile_pic == "f"] = 0
scoringData$host_has_profile_pic[scoringData$host_has_profile_pic == "t"] = 1
scoringData$host_has_profile_pic[scoringData$host_has_profile_pic == "f"] = 0
data$host_has_profile_pic = as.numeric(data$host_has_profile_pic)
scoringData$host_has_profile_pic = as.numeric(scoringData$host_has_profile_pic)


data$host_identity_verified[data$host_identity_verified == "t"] = 1
data$host_identity_verified[data$host_identity_verified == "f"] = 0
scoringData$host_identity_verified[scoringData$host_identity_verified == "t"] = 1
scoringData$host_identity_verified[scoringData$host_identity_verified == "f"] = 0
data$host_identity_verified = as.numeric(data$host_identity_verified)
scoringData$host_identity_verified = as.numeric(scoringData$host_identity_verified)

 
data$is_location_exact[data$is_location_exact == "t"] = 1
data$is_location_exact[data$is_location_exact == "f"] = 0
scoringData$is_location_exact[scoringData$is_location_exact == "t"] = 1
scoringData$is_location_exact[scoringData$is_location_exact == "f"] = 0
data$is_location_exact = as.numeric(data$is_location_exact)
scoringData$is_location_exact = as.numeric(scoringData$is_location_exact)


data$has_availability[data$has_availability == "t"] = 1
data$has_availability[data$has_availabilityt == "f"] = 0
scoringData$has_availability[scoringData$has_availability == "t"] = 1
scoringData$has_availability[scoringData$has_availability == "f"] = 0
data$has_availability = as.numeric(data$has_availability)
scoringData$has_availability = as.numeric(scoringData$has_availability)

data$requires_license[data$requires_license == "t"] = 1
data$requires_license[data$requires_license == "f"] = 0
scoringData$requires_license[scoringData$requires_license == "t"] = 1
scoringData$requires_license[scoringData$requires_license == "f"] = 0
data$requires_license = as.numeric(data$requires_license)
scoringData$requires_license = as.numeric(scoringData$requires_license)



data$instant_bookable[data$instant_bookable == "t"] = 1
data$instant_bookable[data$instant_bookable == "f"] = 0
scoringData$instant_bookable[scoringData$instant_bookable == "t"] = 1
scoringData$instant_bookable[scoringData$instant_bookable == "f"] = 0
data$instant_bookable = as.numeric(data$instant_bookable)
scoringData$instant_bookable = as.numeric(scoringData$instant_bookable)



data$require_guest_phone_verification[data$require_guest_phone_verification == "t"] = 1
data$require_guest_phone_verification[data$require_guest_phone_verification == "f"] = 0
scoringData$require_guest_phone_verification[scoringData$require_guest_phone_verification == "t"] = 1
scoringData$require_guest_phone_verification[scoringData$require_guest_phone_verification == 'f'] = 0
data$require_guest_phone_verification = as.numeric(data$require_guest_phone_verification)
scoringData$require_guest_phone_verification = as.numeric(scoringData$require_guest_phone_verification)

data$is_business_travel_ready[data$is_business_travel_ready == "t"] = 1
data$is_business_travel_ready[data$is_business_travel_ready == "f"] = 0
scoringData$is_business_travel_ready[scoringData$is_business_travel_ready == "t"] = 1
scoringData$is_business_travel_ready[scoringData$is_business_travel_ready == 'f'] = 0
data$is_business_travel_ready = as.numeric(data$is_business_travel_ready)
scoringData$is_business_travel_ready = as.numeric(scoringData$is_business_travel_ready)
```




################# Imput NA as 0 ################################################

```{r}
data$cleaning_fee[is.na(data$cleaning_fee)] = 0
scoringData$cleaning_fee[is.na(scoringData$cleaning_fee)] = 0

data$security_deposit[is.na(data$security_deposit)] = 0
scoringData$security_deposit[is.na(scoringData$security_deposit)] = 0

data$beds[is.na(data$beds)] = 0
scoringData$beds[is.na(scoringData$beds)] = 0

data$reviews_per_month[is.na(data$reviews_per_month)]= 0
scoringData$reviews_per_month[is.na(scoringData$reviews_per_month)] = 0


data$host_is_superhost[is.na(data$host_is_superhost)] = 0
scoringData$host_is_superhost[is.na(scoringData$host_is_superhost)] = 0

scoringData$reviews_per_month[is.na(scoringData$reviews_per_month)] = 0

data$host_response_time[is.na(data$host_response_time)] = 0

data$is_business_travel_ready[is.na(data$is_business_travel_ready)] = 0
scoringData$is_business_travel_ready[is.na(scoringData$is_business_travel_ready)] = 0

data$host_has_profile_pic[is.na(data$host_has_profile_pic)] = 0
scoringData$host_has_profile_pic[is.na(scoringData$host_has_profile_pic)] = 0

data$host_identity_verified[is.na(data$host_identity_verified)] = 0
scoringData$host_identity_verified[is.na(scoringData$host_identity_verified)] = 0
```



#############################  cleaning Data  #######################################

```{r}
library(VIM)
data1<-kNN(data, variable = c('cleaning_fee','security_deposit','beds'), metric = NULL, k = 5,
           dist_var = colnames(data), weights = NULL, numFun = median,
           catFun = maxCat, makeNA = NULL, NAcond = NULL, impNA = TRUE,
           donorcond = NULL, mixed = vector(), mixed.constant = NULL,
           trace = FALSE, imp_var = TRUE, imp_suffix = "imp", addRandom = FALSE,
           useImputedDist = TRUE, weightDist = FALSE)

scoringdata1<-kNN(scoringData, variable = c('cleaning_fee','security_deposit','beds'), metric = NULL, k = 5,
                  dist_var = colnames(scoringData), weights = NULL, numFun = median,
                  catFun = maxCat, makeNA = NULL, NAcond = NULL, impNA = TRUE,
                  donorcond = NULL, mixed = vector(), mixed.constant = NULL,
                  trace = FALSE, imp_var = TRUE, imp_suffix = "imp", addRandom = FALSE,
                  useImputedDist = TRUE, weightDist = FALSE)

data$cleaning_fee<-data1$cleaning_fee
scoringData$cleaning_fee<-scoringdata1$cleaning_fee
data$security_deposit<-data1$security_deposit
scoringData$security_deposit<-scoringdata1$security_deposit
data$beds<-data1$beds
scoringData$beds<-scoringdata1$beds
```



########################## cleaning property_type ########################### 

```{r}
data$property_type[!data$property_type=='Apartment'&
                     !data$property_type=='House'&
                     !data$property_type=='Loft'&
                     !data$property_type=='Condominium'&
                     !data$property_type=='Townhouse']<-'Other'

scoringData$property_type[!scoringData$property_type=='Apartment'&
                            !scoringData$property_type=='House'&
                            !scoringData$property_type=='Loft'&
                            !scoringData$property_type=='Condominium'&
                            !scoringData$property_type=='Townhouse']<-'Other'

data$property_type<-as.factor(data$property_type)

scoringData$property_type<-as.factor(scoringData$property_type)

scoringData$property_type<-factor(scoringData$property_type,levels=levels(data$property_type))


```






############################  creating new variables by using host response time ####################

```{r}
library(stringr)
data$hour = str_detect(data$host_response_time, 'hour')
scoringData$hour = str_detect(scoringData$host_response_time, 'hour')
data$hour = as.numeric(data$hour)
scoringData$data = as.numeric(scoringData$hour)
cor(data$hour, data$price)

data$hours = str_detect(data$host_response_time, 'hours')
scoringData$hours = str_detect(scoringData$host_response_time, 'hours')
data$hours = as.numeric(data$hours)
scoringData$data = as.numeric(scoringData$data)
cor(data$hours, data$price)

data$day = str_detect(data$host_response_time, 'day')
scoringData$day = str_detect(scoringData$host_response_time, 'day')
data$day = as.numeric(data$day)
scoringData$day = as.numeric(scoringData$day)
cor(data$price, data$day)
```



############################ creating new variables by using amenities ############################

```{r}
library(stringr)
data$freeP = str_detect(data$amenities, 'Free street parking')
scoringData$freeP = str_detect(scoringData$amenities, 'Free street parking')
data$freeP = as.numeric(data$freeP)
scoringData$freeP = as.numeric(scoringData$freeP)
cor(data$freeP, data$price)

data$famkid = str_detect(data$amenities, 'Family/kid friendly')
scoringData$famkid = str_detect(scoringData$amenities, 'Family/kid friendly')
data$famkid = as.numeric(data$famkid)
scoringData$famkid = as.numeric(scoringData$famkid)
cor(data$famkid, data$price)


data$fp = str_detect(data$amenities,'Indoor fireplace')
scoringData$fp = str_detect(scoringData$amenities,'Indoor fireplace')
data$ifp = as.numeric(data$fp)
scoringData$fp = as.numeric(scoringData$fp)
cor(data$ifp,data$price)


data$ti = str_detect(data$amenities,c('Cable TV','Internet'))
scoringData$ti = str_detect(scoringData$amenities,c('Cable TV','Internet'))
data$ti = as.numeric(data$ti)
scoringData$ti = as.numeric(scoringData$ti)
cor(data$ti,data$price)

data$gt = str_detect(data$amenities,c('Gym','TV'))
scoringData$gt = str_detect(scoringData$amenities,c('Gym','TV'))
data$gt = as.numeric(data$gt)
scoringData$gt = as.numeric(scoringData$gt)
cor(data$gt,data$price)


data$wd = str_detect(data$amenities,c('Washer','Dryer'))
scoringData$wd = str_detect(scoringData$amenities,c('Washer','Dryer'))
data$wd = as.numeric(data$wd)
scoringData$wd = as.numeric(scoringData$wd)
cor(data$wd,data$price)


data$tct = str_detect(data$amenities,c('TV','Cable TV'))
scoringData$tct = str_detect(scoringData$amenities,c('TV','Cable TV'))
data$tct = as.numeric(data$tct)
scoringData$tct = as.numeric(scoringData$tct)
cor(data$tct,data$price)

data$iron = str_detect(data$amenities,'iron')
scoringData$iron = str_detect(scoringData$amenities,'iron')
data$iron = as.numeric(data$iron)
scoringData$iron = as.numeric(scoringData$iron)
cor(data$iron,data$price)

data$ih = str_detect(data$amenities,c('Iron','Hair dryer'))
scoringData$ih = str_detect(scoringData$amenities,c('Iron','Hair dryer'))
data$ih = as.numeric(data$ih)
scoringData$ih = as.numeric(scoringData$ih)
cor(data$ih,data$price)

data$lt = str_detect(data$amenities,c('Laptop','TV'))
scoringData$lt = str_detect(scoringData$amenities,c('Laptop','TV'))
data$lt = as.numeric(data$lt)
scoringData$lt = as.numeric(scoringData$lt)
cor(data$lt,data$price)

data$dm = str_detect(data$amenities,'Doorman')
scoringData$dm = str_detect(scoringData$amenities,'Doorman')
data$dm = as.numeric(data$dm)
scoringData$dm = as.numeric(scoringData$dm)
cor(data$dm,data$price)


data$wc = str_detect(data$amenities,'Wheelchair')
scoringData$wc = str_detect(scoringData$amenities,'Wheelchair')
data$wc = as.numeric(data$wc)
scoringData$wc = as.numeric(scoringData$wc)
cor(data$wc,data$price)

data$d = str_detect(data$amenities,'Air conditioning')
scoringData$d = str_detect(scoringData$amenities,'Air conditioning')
data$d = as.numeric(data$d)
scoringData$d = as.numeric(scoringData$d)
cor(data$d,data$price)

data$bu = str_detect(data$amenities,'Buzzer')
scoringData$bu = str_detect(scoringData$amenities,'Buzzer')
data$bu = as.numeric(data$bu)
scoringData$bu = as.numeric(scoringData$bu)
cor(data$bu,data$price)

data$fe = str_detect(data$amenities,'fire')
scoringData$fe = str_detect(scoringData$amenities,'fire')
data$fe = as.numeric(data$fe)
scoringData$fe = as.numeric(scoringData$fe)
cor(data$fe, data$price)
```


#######################using information from description and summary ##############################

```{r}
library(stringr)
data$lux = str_detect(data$summary,'luxurious')
scoringData$lux = str_detect(scoringData$summary,'luxurious')
data$lux = as.numeric(data$lux)
scoringData$lux = as.numeric(scoringData$lux)
cor(data$lux,data$price)

data$reno = str_detect(data$summary,'renovated')
scoringData$reno = str_detect(scoringData$summary,'renovated')
data$reno = as.numeric(data$reno)
scoringData$reno = as.numeric(scoringData$reno)
cor(data$reno,data$price)

data$clean = str_detect(data$summary,'clean')
scoringData$clean = str_detect(scoringData$summary,'clean')
data$clean = as.numeric(data$clean)
scoringData$clean = as.numeric(scoringData$clean)
cor(data$clean,data$price)

data$cozy = str_detect(data$summary, 'cozy')
scoringData$cozy = str_detect(scoringData$summary, 'cozy')
data$cozy = as.numeric(data$cozy)
scoringData$cozy = as.numeric(scoringData$cozy)
cor(data$cozy, data$price)

data$terrace = str_detect(data$summary, 'terrace')
scoringData$terrace = str_detect(scoringData$summary, 'terrace')
data$terrace = as.numeric(data$terrace)
scoringData$terrace = as.numeric(scoringData$terrace)
cor(data$terrace, data$price)

data$threebrm = str_detect(data$summary, '3 bedroom')
scoringData$threebrm = str_detect(scoringData$summary, '3 bedroom')
data$threebrm = as.numeric(data$threebrm)
scoringData$threebrm = as.numeric(scoringData$threebrm)
cor(data$threebrm, data$price)

data$gplx = str_detect(data$summary, 'garden duplex')
scoringData$gplx = str_detect(scoringData$summary, 'garden duplex')
data$gplx = as.numeric(data$gplx)
scoringData$gplx = as.numeric(scoringData$gplx)
cor(data$gplx, data$price)

data$cp = str_detect(data$summary, 'central park')
scoringData$cp = str_detect(scoringData$summary, 'central park')
data$cp = as.numeric(data$cp)
scoringData$cp = as.numeric(scoringData$cp)
cor(data$cp, data$price)


data$dsc = str_detect(data$description,'private')
scoringData$dsc = str_detect(scoringData$description,'private')
data$dsc = as.numeric(data$dsc)
scoringData$dsc = as.numeric(scoringData$dsc)
cor(data$dsc,data$price)

data$quiet = str_detect(data$neighborhood_overview,'quiet')
scoringData$quiet = str_detect(scoringData$neighborhood_overview,'quiet')
data$quiet = as.numeric(data$quiet)
scoringData$quiet = as.numeric(scoringData$quiet)
cor(data$quiet,data$price)

data$spacious = str_detect(data$description,'spacious')
scoringData$spacious = str_detect(scoringData$description,'spacious')
data$spacious = as.numeric(data$spacious)
scoringData$spacious = as.numeric(scoringData$spacious)
cor(data$spacious,data$price)
```



#####feature selection################## rmse = 81.39929
```{r}
library(glmnet)
x = model.matrix(price~neighbourhood_group_cleansed+
                   security_deposit+
                   instant_bookable+
                   calculated_host_listings_count+
                   reviews_per_month+availability_30+
                   availability_365+
                   minimum_nights+
                   maximum_nights+
                   host_has_profile_pic+
                   bed_type+
                   is_location_exact+
                   guests_included+
                   extra_people+
                   room_type+
                   property_type+
                   bedrooms+
                   bathrooms+
                   beds+
                   accommodates+
                   cleaning_fee+
                   cancellation_policy+
                   is_business_travel_ready+
                   fp+
                   ti+
                   host_is_superhost+
                   review_scores_location+
                   terrace+
                   cp+
                   threebrm+
                   host_identity_verified,data=data)

y = data$price
fit = glmnet(x,y, alpha=1) 
cv.lasso = cv.glmnet(x,y,alpha=1) 
lambda_best = cv.lasso$lambda.min
cvfit = glmnet(x,y, alpha = 1, lambda = lambda_best, standardize = TRUE)
pred_lassodata = predict(cvfit,s = lambda_best,newx = x)
plot(fit,xvar='lambda',label=T)
plot(fit,xvar='dev',label=T)
 
plot(cv.lasso)
coef(cv.lasso)

rmse = mean(sqrt(cv.lasso$cvm))

```



##### XGBoost ####################################

```{r}
library(xgboost)
library(readr)
library(stringr)
library(caret)
library(car)
```



###counting the number of amenities
```{r}
a = strsplit(as.character(data$amenities), ",")
b = c()
for (i in 1:length(a)){
  b[i] = length(a[[i]])
}
data$num_amenities = b
a1 = strsplit(as.character(scoringData$amenities), ",")
b1 = c()
for (i in 1:length(a1)){
  b1[i] = length(a1[[i]])
}
scoringData$num_amenities = b1
cor(data$num_amenities,data$price)
```


#matrix for data

```{r}
data40= subset(data, select = c(price,
                                num_amenities,
                                square_feet,
                                weekly_price,
                                host_response_time,
                                host_response_rate,
                                review_scores_rating,
                                availability_60,
                                availability_90,
                                neighbourhood_group_cleansed,
                                security_deposit,
                                calculated_host_listings_count,
                                reviews_per_month,
                                availability_30,
                                availability_365,
                                minimum_nights,
                                maximum_nights,
                                is_location_exact,
                                guests_included,
                                extra_people,
                                room_type,
                                property_type,
                                bedrooms,
                                bathrooms,
                                beds,
                                accommodates,
                                cleaning_fee,
                                cancellation_policy,
                                is_business_travel_ready,
                                fp,
                                host_is_superhost,
                                d,lt,ih,dm,wc,ti,gt,bu,lux,
                                host_identity_verified))
```




######split into train and test data#########

```{r}
library(caret)
set.seed(1070)
lala<-createDataPartition(data40$price,p = 0.7,list=FALSE,groups = 100)
train<-data40[lala,]
test<-data40[-lala,]
```








#matrix for scoringData
```{r}
scoringData$price = NA
scoringData40=subset(scoringData,select=c(price,
                                          num_amenities,
                                          square_feet,
                                          weekly_price,
                                          host_response_time,
                                          host_response_rate,
                                          review_scores_rating,
                                          availability_60,
                                          availability_90,
                                          neighbourhood_group_cleansed,
                                          security_deposit,
                                          calculated_host_listings_count,
                                          reviews_per_month,
                                          availability_30,
                                          availability_365,
                                          minimum_nights,
                                          maximum_nights,
                                          is_location_exact,
                                          guests_included,
                                          extra_people,
                                          room_type,
                                          property_type,
                                          bedrooms,
                                          bathrooms,
                                          beds,
                                          accommodates,
                                          cleaning_fee,
                                          cancellation_policy,
                                          is_business_travel_ready,
                                          fp,
                                          host_is_superhost,
                                          d,lt,ih,dm,wc,ti,gt,bu,lux,
                                          host_identity_verified))
```






#cross validation to tune parameters
```{r}
cv.res=xgb.cv(data = data.matrix(train[,-1]),nfold=5,label = train$price,nround=3000, objective="reg:linear")
```

#parameters for my final model
```{r}
xgb<- xgboost(data = data.matrix(train[,-1]), 
                 label = train$price, 
                 eta = 0.01,gamma=0,
                 max_depth = 7,
                 nround=6000, 
                 objective="reg:linear",
                 early_stopping_rounds=50,
                 print_every_n=500,
                 subsample = 0.5,
                 seed =1)
 
```

 

#train rmse : 22.946
```{r}
predxgb<-predict(xgb,newdata=data.matrix(train[,-1]))
RMSE(train$price, predxgb)
```

#test rmse : 63.12298
```{r}
predxgb1<-predict(xgb,newdata=data.matrix(test[,-1]))
RMSE(test$price,predxgb1)
```


#running the same model on whole dataset
```{r}
xgb1<- xgboost(data = data.matrix(data40[,-1]), 
                  label = data40$price, 
                  eta = 0.1,
                  gamma=0,
                  max_depth = 7,
                  nround=6000, 
                  objective="reg:linear",
                  early_stopping_rounds=50,
                  print_every_n=500,
                  subsample = 0.5,
                  set.seed (1))

summary(xgb1)
```

#RMSE for data 
```{r}
predxgb2<-predict(xgb1,newdata=data.matrix(data40[,-1]))
RMSE(data40$price,predxgb2)
```




#predictions on scoringData

```{r}
predxb3<-predict(xgb1,newdata=data.matrix(scoringData40[,-1]))
predxb3
```

#submission public RMSE: 67.75776. private RMSE: 61.29345
```{r}
submissionFile= data.frame(id = scoringData$id, price = predxb3)
write.csv(submissionFile, 'sample_submission5.csv',row.names = F) 
```


